Timeliness of security updates for Android

### 2014-07-30 securityupdates.tex
Add some related work

\section{Related work}
\label{sec:related}
Stopping root exploits working: SEAndroid, Capsicum, iOS.
Detecting malware: Android antivirus useless.

\section{Conclusion}
\label{sec:conclusion}

>>>>

\section{Related work}
\label{sec:related}
We found that since 2011 \daMeanInsecurityPerc\ of devices on average were exposed to known root vulnerabilities, in 2011 Felt et al.\ studied 6 Android handsets and found that they were exposed to root vulnerabilities at least 74\% of the time.
This might indicate that over the last 3 years the security of Android has improved, but the data are not directly comparable.
They also found that 4 of the 46 malware samples (8\%) they analysed contained root exploits, much lower than rates found in later larger studies which found rates of 36.7\%~\cite{Zhou2012b} and 40\%~\cite{Zhou2012a}.

There are continuing efforts to reduce the impact of root vulnerabilities, both in Android and more widely.
SEAndroid~\cite{Smalley2013} which is included in Android from version ???~\cite{TODO} claimed to prevent some root vulnerabilities and to reduce the impact of others.
Capability based enforcement systems such as Capsicum~\cite{Watson2010} substantially reduce the capabilities that an exploit has to try and gain increased privilege with.
When Capsicum is included in Linux~\cite{TODO} and hence in Android, it could be used to place fine grained restrictions on system daemons, preventing vulnerabilities becoming root vulnerabilities.

The security protections used in iOS such as only allowing signed code to run, jails and reviewing of apps has resulted in a lower level of malware affecting iOS~\cite{TODO} but can still be bypassed~\cite{Wang2013a}. %TODO look at iOS protections again and tighten this up

Various attempts have been made to detect malware, %TODO
However DroidChameleon~\cite{Rastogi2013} found that antivirus products could not detect malware if it was simply automatically permuted.

Finding vulnerabilities is frequently a time consuming manual process but, Brumley et al.~\cite{Brumley2008} showed that it is possible to automatically generate exploits from binary patches.
In a similar way some of the vulnerabilities which have been exploited were publicly found by examining the commit made to the Android which fixed the vulnerability.
The update process itself can allow Android apps to gain privilege~\cite{Xing2014} by registering for new permissions before the update which creates that permission is installed.
The Woodpecker tool~\cite{Grace2012} automatically finds permission leaks in stock Android phone images.

\section{Conclusion}
\label{sec:conclusion}
Google Play services
